---
title: "STATS 503 Project"
output: html_notebook
---

# Exploratory data analysis
```{r}
library(ggplot2)
library(plotly)
library(reshape2)

# First let's look at the data summary
df = read.csv(file='data.csv')
print(head(df, 10))
summary(df)

# We may be interested in predicting the last feature -> Revenue
#data$Revenue = factor(data$Revenue)
```
Looking at the data summary, there are 10 numerical and 8 categorical attributes. Assuming that the `Revenue` variable is the class of interest:

Continuous variables:
  * Administrative
  * Administrative duration
  * Informational
  * Informational duration
  * Product Related
  * Product Related duration
  * Bounce rate
  * Exit rate
  * Page value
  * Special day
  
Categorical variables (7 -> not including the target (Revenue)):
  * Operating system
  * Browser
  * Region
  * Traffic type
  * Visitor type
  * Month
  * Weekend

```{r}
# Create boxplots with respect to revenue as our variable of interest and each continuous variable
#df = melt(data, id.var="Revenue")
#p = ggplot(df, aes(x=variable, y=value)) + 
#             geom_boxplot()# + 
             #geom_jitter()
#ggplotly(p)
#p
```
```{r}
# Silly toy plot
ggplot(data=df, aes(x=Revenue, fill=Revenue)) +
  geom_bar()

# Revenue versus bounce rate
ggplot(data=df, aes(x=Revenue, y=BounceRates, fill=Revenue)) +
  geom_bar(stat="identity")
```

```{r fig.width=100%, fig.height=100%}
# Create barplots for all variables now
df2 = melt(df, id.var="Revenue")
print(df2)
p = ggplot(data=df2, aes(x=Revenue, y=value, fill=Revenue, label=variable)) + 
    geom_bar(stat="identity") +
    facet_grid(. ~ variable, 
               scales="free_x", space="free_x", 
               margins=TRUE,   as.table=TRUE) + 
    scale_fill_viridis_d() +
    theme(axis.text.x=element_text(angle=90, hjust=1), 
          axis.text.y=element_blank()) + 
    labs(title="Distribution of each variable's contribution to Revenue",
         y="")
p
#ggplotly(p)

```

